---
title: "Hofmann experiment 2"
output: 
  tufte::tufte_handout: default 
  tufte::tufte_html: default 
date: "2023-06-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(nullabor)
library(tidyverse)
```

# Setting 

- Objective: investigate the power of four competing designs, in assessing a mean shift between distributions 
- Hypotheses for each lineup are: 
  - $H_0$: centers of the two groups are the same 
  - $H_a$: centers of the blue group is shifted to the right (blue group is group 2) 
- factors: 
  - size of the shift between two distributions $d \in \{0.4, 0.6, 0.8, 1.0, 1.2\}$ (5 levels)
  - size of the larger group: $n_1 \in \{15, 45, 135\}$ (3 levels)
  - relative size of the second group: $r \in \{1/3, 2/3, 3/3\}$ (3 levels); 
  $n_2 = r\cdot n_1$
  - 3 replicated data sets; sampled from exponential distributions with $\lambda_1 = 1$ and $\lambda_2 = 1/(d+1)$ 
  - 4 graph types: boxplots, density plots, histograms, dotplots 

How to read the stimuli: 

- images are indexed by numbers from 1 to 20, as well as a subindex of 0 or 1, indicating whether it was the true plot or not. 
- each image is contained in two folders
  - the outer folder contains information about the data set; for example, a folder of the name `d0.8n135r0.33rep2` tells you that the data of each image in this folder corresponds to the data set generated with factors $d = 0.8, n_1 = 135, r = 1/3$ and is the second replication of a total of three replications. 
  - the inner folder contains information about which plot type; there are a total of 4 possible plot types: `box`, `den`, `dot`, and `hist` 


```{r}
d <- 0.4# size of the shift between distributions 
n1 <- 15 # size of the fitst group of points 
r <- 1/3 # ratio between n1 and n2 
n2 <- r * n1 
data1 <- rexp(n1, 1)
data2 <- rexp(n2, 1/(d + 1)) 
```
  
The authors associate a "difficulty" level with lineups from 1 to 9, using the $p$-value corresponding to the difference in means between the two groups in the simulated data sets: 

```{r}
result <- t.test(data1, data2)
result 
```
  

# Charts 

## Boxplot: 

```{r fig.margin=TRUE}
# Combine the samples into one dataframe: 
# combined data 
c_df <- data.frame(
  Value = c(data1, data2),
  Group = factor(c(rep("1", n1), rep("2", n2)))
)
ggplot(c_df, aes(x = Value, y = Group, fill = Group, color = Group)) +
  geom_boxplot(alpha=0.5) +
  xlab("") + 
  ylab("") + 
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```

Using the `nullabor` package, we can generate a lineup graph. Also, based on figure 3 in the original picture, it is safe to assume that the task each participant saw was: In which plot is the blue group furthest to the right?  

```{r, fig.fullwidth=TRUE}
d <- lineup(null_permute("Value"), c_df)
ggplot(d, aes(x = Value, y = Group, fill = Group, color = Group)) +
  geom_boxplot(alpha=0.5) +
  facet_wrap(~ .sample) + 
  xlab("") + 
  ylab("") + 
  theme(legend.position = "none", 
        axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())
```

The position of the true graph (i.e., the un-permutated one), is: 
```{r}
attr(d, "pos") # position of actual graph 
```

## Density plot 

```{r, fig.margin=TRUE}
ggplot(c_df, aes(x = Value, color = Group, fill = Group)) +
  geom_density(alpha=0.5) + 
  ylab("") + 
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```

A sample lineup looks as follows: 
```{r, fig.fullwidth=TRUE}
ggplot(d, aes(x = Value, color = Group, fill = Group)) +
  geom_density(alpha=0.5) + 
  facet_wrap(~ .sample) + 
  ylab("") + 
  theme(legend.position = "none", 
        axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())
```

## Histogram 

```{r, fig.margin=TRUE}
ggplot(c_df, aes(x = Value, fill = Group)) +
  geom_histogram(alpha=0.5, stat = "bin", bins = 10) +
  ylab("") + 
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```

A sample lineup chart looks like follows: 

```{r, fig.fullwidth=TRUE}
ggplot(d, aes(x = Value, fill = Group)) +
  geom_histogram(alpha=0.5, stat = "bin", bins = 10) +
  facet_wrap(~ .sample) + 
  theme(legend.position = "none", 
        axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())
```

## Dotplot 

```{r, fig.margin=TRUE}
ggplot(c_df, aes(x = Value, y = Group, color = Group)) +
  geom_jitter(alpha=0.5, height = 0.05) + 
  ylab("") + 
  theme(legend.position = "none", 
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```

Sample lineup looks as follows: 

```{r, fig.fullwidth=TRUE}
ggplot(d, aes(x = Value, y = Group, color = Group)) +
  geom_jitter(alpha=0.5, height = 0.05) + 
  facet_wrap(~ .sample) + 
  theme(legend.position = "none", 
        axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())
```



